From textual to structured Web API Descriptions\\ \large Knowledge Discovery and Data Mining Seminar 2017

### 2017-08-29 Paper/Paper_KDD.tex
lücken markiert

% *** CITATION PACKAGES ***
%
\usepackage{cite}
% cite.sty was written by Donald Arseneau
% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
% \cite{} output to follow that of the IEEE. Loading the cite package will
% result in citation numbers being automatically sorted and properly
% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
% \cite will automatically add leading space, if needed. Use cite.sty's
% noadjust option (cite.sty V3.8 and later) if you want to turn this off
% such as if a citation ever needs to be enclosed in parenthesis.
% cite.sty is already installed on most LaTeX systems. Be sure and use
% version 5.0 (2009-03-20) and later if using hyperref.sty.
% The latest version can be obtained at:
% http://www.ctan.org/pkg/cite
% The documentation is contained in the cite.sty file itself.

@@

% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  % \usepackage[pdftex]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../pdf/}{../jpeg/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\else
  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
  % will default to the driver specified in the system graphics.cfg if no
  % driver is specified.
  % \usepackage[dvips]{graphicx}
  % declare the path(s) where your graphic files are
  % \graphicspath{{../eps/}}
  % and their extensions so you won't have to specify these with
  % every instance of \includegraphics
  % \DeclareGraphicsExtensions{.eps}
\fi

% *** MATH PACKAGES ***
\usepackage{amsmath}
\usepackage{scrextend}
\usepackage{algorithm}
\usepackage{algorithmic}

@@

\section{Datasets and Crawling}
%rechtsbündige grafik
%\piccaption{Amount of working links in Programmable Web} 
%\parpic[r]{\includegraphics[width=1.5in]{img/pie.png}} 
Prior to our research and development, we looked for suitable datasets with good quality. There was not much research done in this field, therefore we had to look for different alternatives, which will be described in the following Sections. Section II.A describes the Linked Web API dataset and the issues. Section II.B deals with the dataset crawled from Programmable Web  \footnote[1]{https://www.programmableweb.com} and Section II.C shows an alternative way to get data from Google.
\begin{figure}[!t]
\centering
\includegraphics[width= 2in]{img/pie.png}
\caption{Amount of working links in Programmable Web}
\label{fig_sim}
\end{figure}

@@

N is the total number of API descriptions and df(d,t) the document frequency, the number of documents in which a term t appears. 
With the TF-IDF Vectorizer terms with a high term frequency but a low document frequency have the highest tf-idf-value and can be considered more important than terms with a lower tf-idf-value. The result of the vectorization is a spars matrix with xx dimensions.

@@

\subsection{API Clustering}
For the correlation matrix we tried to implement the algorithm introduced by Jian Wu, Liang Chen, Zibin Zheng, Michael R. Lyu and Zhaohui Wu in their Paper “Clustering Web services to facilitate service discovery”. The algorithm determines the similarity of each APIs word-vector with all the other word vectors by comparing the word in the word-vector with the normalized google distance. As a result, the algorithm produces a correlation-matrix where for any given API the distance to each other API can be withdrawn.

\begin{algorithm}[H]
 \caption{Algorithm for API Clustering}
 \begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE word-vectors of the APIs
 \ENSURE  Correlation matrix
 \\ \textit{Procedure} :
  \STATE Calculate for each API combination s1 and s2
 \STATE Accumulate the to a correlation matrix
 %\\ \textit{LOOP Process}
  %\FOR {$i = l-2$ to $0$}
  %\STATE statements..
  %\IF {($i \ne 0$)}
  %\STATE statement..
  %\ENDIF
  %\ENDFOR
 %\RETURN $P$
 \end{algorithmic}
 \end{algorithm}

@@

\begin{algorithm}[H]
 \caption{Algorithm for Density Based Clustering}
 \begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE given number of neighbours required for a point to be dense, maximum distance between two
neighbours in a cluster, word-vectors of the APIs
 \ENSURE  Clusters with associated APIs
 \\ \textit{Procedure} :
  \STATE Arbitrarily choose an initial API $s_1$
 \STATE Mark s 1 and calculate the number of neighbours N in the distance ε
%...
% Das musst du irgendwie noch geschickter darstellen
 \end{algorithmic}
 \end{algorithm}

@@

\begin{algorithm}[H]
 \caption{Algorithm for K-Means}
 \begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE Integer k, word-vectors of the APIs
 \ENSURE  k centres
 \\ \textit{Procedure} :
  \STATE Arbitrarily choose an initial k centres $C = {c_1, c_2, ..., c_k}$.
 \STATE For each $i \in {1, ..., k}$, set the cluster Ci to be the set of points in X that are closer to $c_i$ than
they are to $c_j~for ~all ~j ~6= i$.
\STATE For each $i \in {1, . . . , k}$, set $c_i$ to be the centre of mass of all points in $C_i : c_i = 1 |C_i| P x \in C_i x$.
\STATE Repeat Steps 2 and 3 until C no longer changes % Das kann man auch als Loop schreiben

@@

\section{Results}
We run the evaluation with all possible combinations of the predefined values for the parameters. For the number of clusters k, 13 values between $k=1$ to $k=7500$ where chosen. With a k of one, all APIs are in one cluster and with a k of 7500 the average size of a cluster is XX. We used two different metrics for distance measurements, the Euclidian distance and the Cosine distance and did a dimension reduction dim to $dim⁡= 10$, $dim⁡= 100$, $dim⁡=  250$ and  $dim⁡= 500$ dimensions. This leaves us with $13*2*4=104$ clustering cycles. For every cycle the quality measures were calculated.

The comparison of the quality measures revealed, that they suggest different optimal k, regardless of the dim and the distance metric. The Jaccard as well as the Rand statistic have their maximum between $k=20$ and $k=50$ for all dim and distance metric combinations. Whereas the F-measure indicates an optimal number of clusters between $k=300$ and $k=700$.
The low k suggested by the Jaccard coefficient would mean that we have an average cluster size of around XX, which is too high. The optimal k of the Jaccard coefficient is also very close to the number of manually clustered APIs. It is to investigate to what extend the Jaccard coefficient is influenced by the manual clustering. To avoid any bias which might be caused in this case we put the focus of the evaluation on the precision and recall measure and therefore on the F-measure.

@@

\section{Conclusion}

\section{Future Work}
The classification anhand der texte und das Vorgehen funktioniert im Moment sind die ergebnisse aber noch nicht besser als Programmable Web Clustering. Was noch verbessert werden kann: 
Manuelles Clustering Verbessern
Längere Beschreibungstexte
Mehr werte für Parameter einsetzten
Mehr APIs manuell evaluieren
Parameter learning…

\newpage

>>>>

% *** CITATION PACKAGES ***
\usepackage{cite}

@@

% *** MATH PACKAGES ***
\usepackage{amsmath}
\usepackage{scrextend}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{color}

@@

\section{Datasets and Crawling}
%rechtsbündige grafik (habe ich jetzt erst mal rausgenommen, da es komisch aussah):
%\piccaption{Amount of working links in Programmable Web} 
%\parpic[r]{\includegraphics[width=1.5in]{img/pie.png}} 
Prior to our research and development, we looked for suitable datasets with good quality. There was not much research done in this field, therefore we had to look for different alternatives, which will be described in the following Sections. Section II.A describes the Linked Web API dataset and the issues. Section II.B deals with the dataset crawled from Programmable Web  \footnote[1]{https://www.programmableweb.com} and Section II.C shows an alternative way to get data from Google.
\begin{figure}[!t]
\centering
\includegraphics[width= 2in]{img/pie.png}
\caption{Amount of working links in Programmable Web}
\label{fig_sim}
\end{figure}

@@

N is the total number of API descriptions and df(d,t) the document frequency, the number of documents in which a term t appears. 
With the TF-IDF Vectorizer terms with a high term frequency but a low document frequency have the highest tf-idf-value and can be considered more important than terms with a lower tf-idf-value. The result of the vectorization is a spars matrix with \textcolor{red} {XXXXXXX} dimensions.

@@

\subsection{API Clustering}
For the correlation matrix we tried to implement the algorithm introduced by Jian Wu, Liang Chen, Zibin Zheng, Michael R. Lyu and Zhaohui Wu in their Paper “Clustering Web services to facilitate service discovery” \cite{kanungo2002efficient}. The algorithm determines the similarity of each APIs word-vector with all the other word vectors by comparing the word in the word-vector with the normalized google distance. As a result, the algorithm produces a correlation-matrix where for any given API the distance to each other API can be withdrawn.

\begin{algorithm}[H]
 \caption{Algorithm 1}
 \begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE word-vectors of the APIs
 \ENSURE  Correlation matrix
 \\ \textit{Procedure} :
  \STATE Calculate for each API combination s1 and s2
 \STATE Accumulate the to a correlation matrix
% als inspiration ;)
 %\\ \textit{LOOP Process}
  %\FOR {$i = l-2$ to $0$}
  %\STATE statements..
  %\IF {($i \ne 0$)}
  %\STATE statement..
  %\ENDIF
  %\ENDFOR
 %\RETURN $P$
 \end{algorithmic}
 \end{algorithm}

@@

\begin{algorithm}[H]
 \caption{Algorithm 2}
 \begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE given number of neighbours required for a point to be dense, maximum distance between two
neighbours in a cluster, word-vectors of the APIs
 \ENSURE  Clusters with associated APIs
 \\ \textit{Procedure} :
  \STATE Arbitrarily choose an initial API $s_1$
 \STATE Mark s 1 and calculate the number of neighbours N in the distance ε
%...
% Das musst du irgendwie noch geschickter darstellen
 \end{algorithmic}
 \end{algorithm}

@@

\begin{algorithm}[H]
 \caption{Algorithm 3}
 \begin{algorithmic}[1]
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
 \renewcommand{\algorithmicensure}{\textbf{Output:}}
 \REQUIRE Integer k, word-vectors of the APIs
 \ENSURE  k centres
 \\ \textit{Procedure} :
  \STATE Arbitrarily choose an initial k centres $C = {c_1, c_2, ..., c_k}$.
 \STATE For each $i \in {1, ..., k}$, set the cluster Ci to be the set of points in X that are closer to $c_i$ than
they are to $c_j~for ~all ~j ~6= i$.
\STATE For each $i \in {1, . . . , k}$, set $c_i$ to be the centre of mass of all points in $C_i : c_i = 1 |C_i| P x \in C_i x$.
\STATE Repeat Steps 2 and 3 until C no longer changes % Das kann man auch als Loop schreiben

@@

\section{Results}
We run the evaluation with all possible combinations of the predefined values for the parameters. For the number of clusters k, 13 values between $k=1$ to $k=7500$ where chosen. With a k of one, all APIs are in one cluster and with a k of 7500 the average size of a cluster is \textcolor{red} {XX}. We used two different metrics for distance measurements, the Euclidian distance and the Cosine distance and did a dimension reduction dim to $dim⁡= 10$, $dim⁡= 100$, $dim⁡=  250$ and  $dim⁡= 500$ dimensions. This leaves us with $13*2*4=104$ clustering cycles. For every cycle the quality measures were calculated.

The comparison of the quality measures revealed, that they suggest different optimal k, regardless of the dim and the distance metric. The Jaccard as well as the Rand statistic have their maximum between $k=20$ and $k=50$ for all dim and distance metric combinations. Whereas the F-measure indicates an optimal number of clusters between $k=300$ and $k=700$.
The low k suggested by the Jaccard coefficient would mean that we have an average cluster size of around \textcolor{red} {XX}, which is too high. The optimal k of the Jaccard coefficient is also very close to the number of manually clustered APIs. It is to investigate to what extend the Jaccard coefficient is influenced by the manual clustering. To avoid any bias which might be caused in this case we put the focus of the evaluation on the precision and recall measure and therefore on the F-measure.

@@

\section{Conclusion}
\textcolor{red} {XXXXXXX}

\section{Future Work}
\textcolor{red} {The classification anhand der texte und das Vorgehen funktioniert im Moment sind die ergebnisse aber noch nicht besser als Programmable Web Clustering. Was noch verbessert werden kann: 
Manuelles Clustering Verbessern
Längere Beschreibungstexte
Mehr werte für Parameter einsetzten
Mehr APIs manuell evaluieren
Parameter learning… }

%\newpage
